The \dealii Library, Version 9.2

### 2020-04-24 9.2/paper.tex
start 9.2

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Thomas C. Clevenger,
    Denis Davydov,
    Marc Fehling,
    Daniel Garcia-Sanchez,
    Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.1, 2019},
}

\title{The \dealii Library, Version 9.1}

\author[*1]{Daniel Arndt}
\affil[1]{Computational Engineering and Energy Sciences Group,
  Computional Sciences and Engineering Division,
  Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
  TN 37831, USA.
  {\texttt{\{arndtd,turcksinbr\}@ornl.gov}}}

\author[2]{Wolfgang~Bangerth}
\affil[2]{Department of Mathematics, Colorado State University, Fort
  Collins, CO 80523-1874, USA.
  {\texttt{bangerth@colostate.edu},
   \texttt{harper@math.colostate.edu}}}

\author[3]{Thomas~C.~Clevenger}
\affil[3]{School of Mathematical and Statistical Sciences,
  Clemson University,
  Clemson, SC, 29634, USA
  {\texttt{\{tcleven, heister\}@clemson.edu}}}

\author[4]{Denis~Davydov}
\affil[4]{Chair of Applied Mechanics,
  Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  Egerlandstr.\ 5,
  91058 Erlangen, Germany.
  {\texttt{\{denis.davydov,jean-paul.pelteret\}@fau.de}}}

\author[5]{Marc~Fehling}
\affil[5]{Institute for Advanced Simulation,
  Forschungszentrum J\"{u}lich GmbH,
  52425 J\"{u}lich, Germany.
  {\texttt{m.fehling@fz-juelich.de}}}

\author[6]{Daniel Garcia-Sanchez}
\affil[6]{Sorbonne Universit\'es, UPMC Univ.\ Paris 06, CNRS-UMR 7588,
  Institut des NanoSciences de Paris, F-75005, Paris, France
  {\texttt{daniel.garcia-sanchez@insp.upmc.fr}}}

\author[2]{Graham Harper}

\author[3,7]{Timo~Heister}
\affil[7]{Scientific Computing and Imaging Institute,
  72 S Central Campus Drive, Room 3750
  Salt Lake City, UT 84112.
  {\texttt{heister@sci.utah.edu}}}
%
\author[8]{Luca~Heltai}
\affil[8]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
  {\texttt{luca.heltai@sissa.it}}}

\author[9]{Martin~Kronbichler}
\affil[9]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[10]{Ross~Maguire~Kynch}
\affil[10]{Zienkiewicz Centre for Computational Engineering,
  College of Engineering, Swansea University,
  Bay Campus, Fabian Way, Swansea SA1 8EN, Wales, UK.
  {\texttt{rkynch@gmail.com}}}

\author[11]{Matthias~Maier}
\affil[11]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[4]{Jean-Paul~Pelteret}

\author[*1]{Bruno~Turcksin}

\author[12]{David Wells}
\affil[12]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

>>>>

\hypersetup{
  pdfauthor={
%     Daniel Arndt,
%     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
%     Martin Kronbichler,
%     Ross Maguire Kynch,
%     Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

\title{The \dealii Library, Version 9.2}

% \author[*1]{Daniel Arndt}
% \affil[1]{Computational Engineering and Energy Sciences Group,
%   Computional Sciences and Engineering Division,
%   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
%   TN 37831, USA.
%   {\texttt{\{arndtd,turcksinbr\}@ornl.gov}}}
% 
% \author[2]{Wolfgang~Bangerth}
% \affil[2]{Department of Mathematics, Colorado State University, Fort
%   Collins, CO 80523-1874, USA.
%   {\texttt{bangerth@colostate.edu},
%    \texttt{harper@math.colostate.edu}}}
% 
% \author[3]{Thomas~C.~Clevenger}
% \affil[3]{School of Mathematical and Statistical Sciences,
%   Clemson University,
%   Clemson, SC, 29634, USA
%   {\texttt{\{tcleven, heister\}@clemson.edu}}}
% 
% \author[4]{Denis~Davydov}
% \affil[4]{Chair of Applied Mechanics,
%   Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen, Germany.
%   {\texttt{\{denis.davydov,jean-paul.pelteret\}@fau.de}}}
% 
% \author[5]{Marc~Fehling}
% \affil[5]{Institute for Advanced Simulation,
%   Forschungszentrum J\"{u}lich GmbH,
%   52425 J\"{u}lich, Germany.
%   {\texttt{m.fehling@fz-juelich.de}}}
% 
% \author[6]{Daniel Garcia-Sanchez}
% \affil[6]{Sorbonne Universit\'es, UPMC Univ.\ Paris 06, CNRS-UMR 7588,
%   Institut des NanoSciences de Paris, F-75005, Paris, France
%   {\texttt{daniel.garcia-sanchez@insp.upmc.fr}}}
% 
% \author[2]{Graham Harper}
% 
\author[3]{Timo~Heister}
 \affil[3]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister@clemson.edu}}}

% %
% \author[8]{Luca~Heltai}
% \affil[8]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
%   {\texttt{luca.heltai@sissa.it}}}
% 
% \author[9]{Martin~Kronbichler}
% \affil[9]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
% 
% \author[10]{Ross~Maguire~Kynch}
% \affil[10]{Zienkiewicz Centre for Computational Engineering,
%   College of Engineering, Swansea University,
%   Bay Campus, Fabian Way, Swansea SA1 8EN, Wales, UK.
%   {\texttt{rkynch@gmail.com}}}
% 
% \author[11]{Matthias~Maier}
% \affil[11]{Department of Mathematics,
%   Texas A\&M University,
%   3368 TAMU,
%   College Station, TX 77845, USA.
%   {\texttt{maier@math.tamu.edu}}}
% 
% \author[4]{Jean-Paul~Pelteret}
% 
% \author[*1]{Bruno~Turcksin}
% 
% \author[12]{David Wells}
% \affil[12]{Department of Mathematics, University of North Carolina,
%   Chapel Hill, NC 27516, USA.
%   {\texttt{drwells@email.unc.edu}}}
